---
title: "S&P 500 Volatility"
author: "Nathan J. Tuttle"
date: "April 4, 2017"
output: 
  word_document:
   pandoc_args: [ 
      "--output=NTuttle_Livesession11assignment.docx" 
    ] 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment 11
# Nathan Tuttle (47243733)
Submit a HTML or WORD file with the github link that contains codes and markdown document, which shows the result. I will look through your HTML/Word file to check out the code and its result. Then, I will check out github link to see if you have a code(s) and markdown document

Link to GitHub page
https://github.com/tuttlen/SP500Volatility.git

Link to RMarkdown
https://github.com/tuttlen/SP500Volatility/blob/master/NTuttle_Livesession11assignment.rmd


```{r volatility}
source("SP500.r")

## S&P 500 (^GSPC)
###    SNP - SNP Real Time Price. Currency in USD

# TODO: Download the data of SP500 '^gspc'.
SNPdata <- get.hist.quote("^GSPC",quote="Close")

# TODO: Calculate the log returns, which is the subtractration of log(lag(SNPdata)) and log(SNPdata)
SNPret <- log(lag(SNPdata)) - log(SNPdata)

# TODO: Calculate volatility measure that is to multiply sd(SNPret),sqrt(250), 100
SNPvol <- sd(SNPret)*sqrt(250)*100


# Calculate volatility over entire length of series for various three different decay factors: 10 30. 100

# TODO: call getVol function with the parameters: 10,SNPret
volest <- getVol(10,SNPret)

# TODO: call getVol function with the parameters: 30,SNPret
volest2 <- getVol(30,SNPret)

# TODO: call getVol function with the parameters: 100,SNPret
volest3 <- getVol(100,SNPret)

# Plot the results, overlaying the volatility curves on the data, just as was done in the S&P example.
plot(volest,type="l")

# TODO: Add connected line segments for volest2 with the parameters: type="l",col="red"
# hint: look at oilExerciseCode.R file at the live discussion
lines(volest2, col="red", type="l")

# TODO: Add connected line segments for volest3 with the parameters: type="l",col="blue"
lines(volest3, col="blue", type="l")
```

# Discussion
In the above plot we see that with 20 degrees of decay there is very little deviation. However, for decay of 30
the blue line leads the index.

